\chapter{Preparing a high-quality PDF from LaTeX}\label{chap:PDFprep}
If the author chooses to complete the publications process using LaTeX\, the author must incorporate feedback and edits in to the LaTeX source files and prepare the final PDF, following these guidelines.

\section{PDF tagging}\label{sec:PDFtagging}
PDF tagging is a process whereby the components of the PDF document (headings, figures, tables, text) are marked so that a document reader can understand the document. This is useful when text to speech converters are being used. The process of tagging is also known as structuring, so that a tagged document might also be referred to as a structured document\footnote{This is a test}.

\LaTeX\ does not prepare a structured PDF document directly.

At this time tags cannot be added reliably within LaTeX. Instead, they should be added after the PDF is compiled using a PDF editor such as Adobe's Acrobat Pro. 

\section{Alternative text}\label{sec:Alttext}
Alternative text, or `Alt text', is a textual description of an equation, link or figure that can be used to replace the visual information in that element. This is often seen as a text `pop-up' in PDF readers. 

At this time Alt text cannot be added reliably withing LaTeX. Instead, it should be added after the PDF is compiled using a PDF editor such as Adobe's Acrobat Pro. 

\section{Embedded fonts}
All fonts should be embedded in the the final PDF. Check the PDF for embedded fonts using a PDF viewer. For example, in Adobe Acrobat Reader, look at the `fonts' tag of the document properties. If any fonts are not shown as being an \emph{embedded subset}, try the conversion again. 

Encapsulated postscript figures are particularly prone to having undefined fonts. Check by compiling the document in draft mode, and seeing if the fonts are still present in the output PDF. To fix this problem, change \emph{.eps} files to \emph{.png} files. To do this `on the fly', use this in the document's preamble:

\begin{lstlisting}
\usepackage{epstopdf}
\epstopdfDeclareGraphicsRule
 {.eps}{png}{.png}{convert eps:\SourceFile.\SourceExt png:\OutputFile}
\AppendGraphicsExtensions{.png}
\end{lstlisting}